Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-05-21 awipev-CO2.Rmd
pH durafet was calculated using depth 11 m... removed unnecessary data frame in the use of pHinsi

# Conversion of spectro pH to insitu mix T°
pH_seafet <- d %>%
  dplyr::filter(!is.na(pH_s_seafet) & !is.na(temp_insitu_ctd) )
pH_seafet <- pH_seafet %>%
  dplyr::mutate(ph_s_sf_temp_mix = pHinsi(pH=pH_seafet$pH_s_seafet,ALK=pH_seafet$at_mean_interp*1e-6, Tinsi=pH_seafet$temp_insitu_ctd, Tlab=pH_seafet$temp_s_lab, Pinsi= pH_seafet$depth/10, S=pH_seafet$sal_mix,Pt=0,Sit=0))

pH_durafet <- d %>%
#  dplyr::filter(!is.na(pH_s_durafet))
    dplyr::filter(!is.na(pH_s_durafet) & !is.na(sal_fb) & !is.na(temp_fb))
pH_durafet <- pH_durafet %>%
  dplyr::mutate(ph_s_dur_temp_fb = pHinsi(pH=pH_durafet$pH_s_durafet, ALK=pH_durafet$at_mean_interp*1e-6, Tinsi=pH_durafet$temp_fb, Tlab=pH_durafet$temp_s_lab, Pinsi= pH_durafet$depth/10, S=pH_durafet$sal_fb, Pt=0, Sit=0))

@@

# To make sf calibration against pH spectro, we need: sal - T insi - voltINT/EXT . If we missed one of these parameters, calibration will not run
# Here we try to fill the gap when it is possible: make a mean with 4 previous/next hours available in the time serie. 
# If the pH spectro is too far from a needed value, we decided to skip it for the calibration.
# we highlighted 7 pH spectro that dont match one of these parameters : 2017-08-24 14:00:00 - 2017-09-28 13:00:00 - 2018-04-16 07:00:00 - 2018-12-14 09:00:00 - 2019-01-18 09:00:00 - 2019-09-13 08:00:00 - 2019-09-13 13:00:00
# (1) Raw voltage INT + pHINT must be filtered from 2017-12-14 to 2018-01-08 < 8.04,
# (2) removed from 2018-01-08 to 2018-02-02
# (3) outliers removed
# (1)
d_all$phINT <- ifelse(d_all$datetime >= as.POSIXct("2017-12-14") &
                        d_all$datetime <= as.POSIXct("2018-01-08") &
                        d_all$phINT < 8.04, NA, d_all$phINT)
d_all$phEXT <-ifelse(d_all$datetime >= as.POSIXct("2017-12-14") &
                       d_all$datetime <= as.POSIXct("2018-01-08") &
                       d_all$phEXT < 8.04, NA, d_all$phEXT) 
d_all$voltINT <-ifelse(d_all$datetime >= as.POSIXct("2017-12-14") &
                         d_all$datetime <= as.POSIXct("2018-01-08") &
                         d_all$voltINT < -0.9439, NA, d_all$voltINT) 
d_all$voltEXT <-ifelse(d_all$datetime >= as.POSIXct("2017-12-14") &
                         d_all$datetime <= as.POSIXct("2018-01-08") &
                         d_all$voltEXT < -0.907, NA, d_all$voltEXT) 
# (2)
d_all$voltINT <- ifelse(d_all$datetime >= as.POSIXct("2018-01-08 17:00:00") &
                          d_all$datetime <= as.POSIXct("2018-02-02 09:00:00"), 
                        NA, d_all$voltINT)
d_all$voltEXT <- ifelse(d_all$datetime >= as.POSIXct("2018-01-08 17:00:00") &
                          d_all$datetime <= as.POSIXct("2018-02-02 09:00:00"),
                        NA, d_all$voltEXT)
d_all$phINT <- ifelse(d_all$datetime >= as.POSIXct("2018-01-08 17:00:00") &
                        d_all$datetime <= as.POSIXct("2018-02-02 09:00:00"),
                      NA, d_all$phINT)
d_all$phEXT <- ifelse(d_all$datetime >= as.POSIXct("2018-01-08 17:00:00") &
                        d_all$datetime <= as.POSIXct("2018-02-02 09:00:00"),
                      NA, d_all$phEXT)
# (3)
d_all$voltINT <- ifelse(d_all$datetime == as.POSIXct("2017-11-02 21:00:00") |
                          d_all$datetime == as.POSIXct("2018-04-18 14:00:00"),
                        NA, d_all$voltINT)
#periode 1, mean of 4 next hours for volt int + T seaF
# mean_voltINT_4h <- d_all %>%
#   dplyr::filter(
#     datetime >= as.POSIXct("2017-08-24 19:00:00") &
#       datetime <= as.POSIXct("2017-08-24 22:00:00")
#   ) %>%
#   dplyr::summarise(mean(voltINT, na.rm = TRUE))
#mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
zz <- d_all %>%
  dplyr::filter(
    datetime >= as.POSIXct("2017-08-24 19:00:00") &
      datetime <= as.POSIXct("2017-08-24 22:00:00")
  )
mean_voltINT_4h <-  mean(zz$voltINT, na.rm = TRUE)
d_all <- d_all %>%
  dplyr::mutate(voltINT = ifelse(
    datetime == as.POSIXct("2017-08-24 13:00:00"),
    mean_voltINT_4h,
    voltINT
  ))
# mean_voltEXT_4h <- d_all %>%
#   dplyr::filter(
#     datetime >= as.POSIXct("2017-08-24 19:00:00") &
#       datetime <= as.POSIXct("2017-08-24 22:00:00")
#   ) %>%
#   dplyr::summarise(mean(voltEXT, na.rm = TRUE))
# mean_voltEXT_4h <- as.numeric(mean_voltEXT_4h)
zz <- d_all %>%
  dplyr::filter(
    datetime >= as.POSIXct("2017-08-24 19:00:00") &
      datetime <= as.POSIXct("2017-08-24 22:00:00")
  )
mean_voltEXT_4h <-  mean(zz$voltEXT, na.rm = TRUE)
d_all <- d_all %>%
  dplyr::mutate(voltEXT = ifelse(
    datetime == as.POSIXct("2017-08-24 13:00:00"),
    mean_voltEXT_4h,
    voltEXT
  ))
# mean_TseaF_4h <- d_all %>%
#   dplyr::filter(
#     datetime >= as.POSIXct("2017-08-24 19:00:00") &
#       datetime <= as.POSIXct("2017-08-24 22:00:00")
#   ) %>%
#   dplyr::summarise(mean(temp_sf, na.rm = TRUE))
# mean_TseaF_4h <- as.numeric(mean_TseaF_4h)
zz <- d_all %>%
  dplyr::filter(
    datetime >= as.POSIXct("2017-08-24 19:00:00") &
      datetime <= as.POSIXct("2017-08-24 22:00:00")
  )
mean_TseaF_4h <-  mean(zz$temp_sf, na.rm = TRUE)
d_all <- d_all %>%
  dplyr::mutate(temp_mix = ifelse(
    datetime == as.POSIXct("2017-08-24 13:00:00"),
    mean_TseaF_4h,
    temp_mix
  ))

>>>>

# Conversion of spectro pH to insitu mix T°
pH_seafet <- d %>%
  dplyr::filter(!is.na(pH_s_seafet) & !is.na(temp_insitu_ctd) )
pH_seafet <- pH_seafet %>%
  dplyr::mutate(ph_s_sf_temp_mix = pHinsi(pH = pH_s_seafet, ALK = at_mean_interp*1e-6, Tinsi = temp_insitu_ctd, Tlab = temp_s_lab, Pinsi = depth/10, S = sal_mix, Pt = 0, Sit = 0))

pH_durafet <- d %>%
#  dplyr::filter(!is.na(pH_s_durafet))
    dplyr::filter(!is.na(pH_s_durafet) & !is.na(sal_fb) & !is.na(temp_fb))
pH_durafet <- pH_durafet %>%
#  dplyr::mutate(ph_s_dur_temp_fb = pHinsi(pH=pH_durafet$pH_s_durafet, ALK=pH_durafet$at_mean_interp*1e-6, Tinsi=pH_durafet$temp_fb, Tlab=pH_durafet$temp_s_lab, Pinsi= pH_durafet$depth/10, S=pH_durafet$sal_fb, Pt=0, Sit=0))
  dplyr::mutate(ph_s_dur_temp_fb = pHinsi(pH = pH_s_durafet, ALK = at_mean_interp*1e-6, Tinsi = temp_fb, Tlab = temp_s_lab, Pinsi = 0, S = sal_fb, Pt = 0, Sit = 0))

@@

# To make sf calibration against pH spectro, we need: sal - T insi - voltINT/EXT . If we missed one of these parameters, calibration will not run
# Here we try to fill the gap when it is possible: make a mean with 4 previous/next hours available in the time serie. 
# If the pH spectro is too far from a needed value, we decided to skip it for the calibration.
# we highlighted 7 pH spectro that dont match one of these parameters : 2017-08-24 14:00:00 - 2017-09-28 13:00:00 - 2018-04-16 07:00:00 - 2018-12-14 09:00:00 - 2019-01-18 09:00:00 - 2019-09-13 08:00:00 - 2019-09-13 13:00:00
# (1) Raw voltage INT + pHINT must be filtered from 2017-12-14 to 2018-01-08 < 8.04,
# (2) removed from 2018-01-08 to 2018-02-02
# (3) outliers removed
# (1)
d_all$phINT <- ifelse(d_all$datetime >= as.POSIXct("2017-12-14") &
                        d_all$datetime <= as.POSIXct("2018-01-08") &
                        d_all$phINT < 8.04, NA, d_all$phINT)
d_all$phEXT <-ifelse(d_all$datetime >= as.POSIXct("2017-12-14") &
                       d_all$datetime <= as.POSIXct("2018-01-08") &
                       d_all$phEXT < 8.04, NA, d_all$phEXT) 
d_all$voltINT <-ifelse(d_all$datetime >= as.POSIXct("2017-12-14") &
                         d_all$datetime <= as.POSIXct("2018-01-08") &
                         d_all$voltINT < -0.9439, NA, d_all$voltINT) 
d_all$voltEXT <-ifelse(d_all$datetime >= as.POSIXct("2017-12-14") &
                         d_all$datetime <= as.POSIXct("2018-01-08") &
                         d_all$voltEXT < -0.907, NA, d_all$voltEXT) 
# (2)
d_all$voltINT <- ifelse(d_all$datetime >= as.POSIXct("2018-01-08 17:00:00") &
                          d_all$datetime <= as.POSIXct("2018-02-02 09:00:00"), 
                        NA, d_all$voltINT)
d_all$voltEXT <- ifelse(d_all$datetime >= as.POSIXct("2018-01-08 17:00:00") &
                          d_all$datetime <= as.POSIXct("2018-02-02 09:00:00"),
                        NA, d_all$voltEXT)
d_all$phINT <- ifelse(d_all$datetime >= as.POSIXct("2018-01-08 17:00:00") &
                        d_all$datetime <= as.POSIXct("2018-02-02 09:00:00"),
                      NA, d_all$phINT)
d_all$phEXT <- ifelse(d_all$datetime >= as.POSIXct("2018-01-08 17:00:00") &
                        d_all$datetime <= as.POSIXct("2018-02-02 09:00:00"),
                      NA, d_all$phEXT)
# (3)
d_all$voltINT <- ifelse(d_all$datetime == as.POSIXct("2017-11-02 21:00:00") |
                          d_all$datetime == as.POSIXct("2018-04-18 14:00:00"),
                        NA, d_all$voltINT)

#periode 1, mean of 4 next hours for volt int + T seaF
# mean_voltINT_4h <- d_all %>%
#   dplyr::filter(
#     datetime >= as.POSIXct("2017-08-24 19:00:00") &
#       datetime <= as.POSIXct("2017-08-24 22:00:00")
#   ) %>%
#   dplyr::summarise(mean(voltINT, na.rm = TRUE))
#mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
zz <- d_all %>%
  dplyr::filter(
    datetime >= as.POSIXct("2017-08-24 19:00:00") &
      datetime <= as.POSIXct("2017-08-24 22:00:00")
  )
mean_voltINT_4h <-  mean(zz$voltINT, na.rm = TRUE)
d_all <- d_all %>%
  dplyr::mutate(voltINT = ifelse(
    datetime == as.POSIXct("2017-08-24 13:00:00"),
    mean_voltINT_4h,
    voltINT
  ))
# mean_voltEXT_4h <- d_all %>%
#   dplyr::filter(
#     datetime >= as.POSIXct("2017-08-24 19:00:00") &
#       datetime <= as.POSIXct("2017-08-24 22:00:00")
#   ) %>%
#   dplyr::summarise(mean(voltEXT, na.rm = TRUE))
# mean_voltEXT_4h <- as.numeric(mean_voltEXT_4h)
zz <- d_all %>%
  dplyr::filter(
    datetime >= as.POSIXct("2017-08-24 19:00:00") &
      datetime <= as.POSIXct("2017-08-24 22:00:00")
  )
mean_voltEXT_4h <-  mean(zz$voltEXT, na.rm = TRUE)
d_all <- d_all %>%
  dplyr::mutate(voltEXT = ifelse(
    datetime == as.POSIXct("2017-08-24 13:00:00"),
    mean_voltEXT_4h,
    voltEXT
  ))
# mean_TseaF_4h <- d_all %>%
#   dplyr::filter(
#     datetime >= as.POSIXct("2017-08-24 19:00:00") &
#       datetime <= as.POSIXct("2017-08-24 22:00:00")
#   ) %>%
#   dplyr::summarise(mean(temp_sf, na.rm = TRUE))
# mean_TseaF_4h <- as.numeric(mean_TseaF_4h)
zz <- d_all %>%
  dplyr::filter(
    datetime >= as.POSIXct("2017-08-24 19:00:00") &
      datetime <= as.POSIXct("2017-08-24 22:00:00")
  )
mean_TseaF_4h <-  mean(zz$temp_sf, na.rm = TRUE)
d_all <- d_all %>%
  dplyr::mutate(temp_mix = ifelse(
    datetime == as.POSIXct("2017-08-24 13:00:00"),
    mean_TseaF_4h,
    temp_mix
  ))
